Reaction-diffusion spatial modeling of COVID-19 in Chicago

### 2021-07-20 draft/chicago-spatial-covid-draft.tex
Include bibliography

At the PDE level, we have not incorporated any functional forms for directional spreading.
In principle, these terms can represent ``daily practices'' (work commutes, etc.), as well as longer temporal or spatial scales (major thoroughfare traffic, etc.).
We simply allow diffusion to perform the relevant spreading.
Arriving infected individuals are assumed to form local hotspots within the susceptible population.
This initial seeding roughly approximates long-range transportation.

>>>>

As in \cite{Kevrekidis_2021}, we have not incorporated any functional forms for directional spreading at the PDE level.
In principle, these terms can represent ``daily practices'' (work commutes, etc.), as well as longer temporal or spatial scales (major thoroughfare traffic, etc.).
We simply allow diffusion to perform the relevant spreading.
Arriving infected individuals are assumed to form local hotspots within the susceptible population.
This initial seeding roughly approximates long-range transportation.

The next step is to identify the parameters at the ODE level.
To do this, we use a nonlinear optimization algorithm.
We determine the optimal parameters by minimizing the Euclidean distance between the time series generated by the model ($\num$) and the corresponding observed ($\obs$) time series,
\begin{equation}
	\N = \sum_i \left( \left| \log(C_\num (t_i)) - \log(C_\obs (t_i)) \right|^2 + \left| \log(R_\num (t_i)) - \log(R_\obs (t_i)) \right|^2 \right)
\end{equation}
where the index $i$ identifies a point in the time series.
The parameters are optimized to reproduce the reported total number of infected cases $C(t) = I(t) + R(t)$, and the total number of removed $R(t)$.

\bibliographystyle{abbrv}
\bibliography{chicago-spatial-covid-draft}
